%-------------------------
% Resume in Latex
% Author : Ravi Yadav
% Website: https://github.com/raviyadv/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Ravi Yadav}} & Email : \href{mailto:tech.raviyadav@gmail.com}{tech.raviyadav@gmail.com}\\
  \href{https://github.com/raviyadv/resume/}{https://github.com/raviyadv/resume} & Mobile : +91-9991368889 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Birla Institute Of Technology}{Mesra, India}
      {Master in Computer Science}{Aug. 2011 -- July. 2014}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {JP Morgan Chase}{Bengaluru, India}
      {Senior Software Engineer}{June 2017 - Present}
      \resumeItemListStart
        \resumeItem{Navigator}
          {Navigator is a unified servicing desktop designed to streamline the client servicing experience through integrated data, intelligent workflow, and intuitive interface design. \\ Env.: Microservices Architecture, K8S, Spring Boot, Spring Reactive, Java, React, REST Web Service, Oracle, Maven, Agile}
        \resumeItem{Welcome}
          {Welcome fundamentally change the onboarding experience for clients to open an account from anywhere, it provides the provision to add products and service online. Trying to avoid the stack of paperwork by e-sign documents, and reducing the process time frame. \\ Env.: Microservice Architecture, Spring, Angular JS, Cloud Foundry, REST Web Service, Java, Oracle, Maven, Agile}
      \resumeItemListEnd

    \resumeSubheading
      {HPE R\&D}{Bengaluru, India}
      {Software Engineer}{Nov 2015 - May 2017}
      \resumeItemListStart
        \resumeItem{AP4SAAS}
          {AP4SaaS is a PaaS cloud platform system where the cloud services are hosted and services are charged on basis of usage. \\ Env.: Monolithic Architecture, Java, SOAP Web Service, JBoss, Spring, JSP, Oracle}
        \resumeItem{DSP}
          {Dynamic SIM Provisioning automate the provisioning of SIM card for the telecom operator. There is an embedded sim card without an IMSI number, it activates the SIM card as per the user's choice and also has the feature to activate a sleeping SIM or dead SIM. \\ Env.: Monolithic Architecture, Java, Spring, JSP, Oracle}
      \resumeItemListEnd

    \resumeSubheading
      {WebTek}{Bengaluru, India}
      {Associate}{Aug 2014 and Oct 2015}
      \resumeItemListStart
        \resumeItem{E-LPG Distribution}
          {A gas distribution application to supply Gas by taking orders online. \\ Env.: Monolithic Architecture, Spring, Java, JSP, MySQL}

  \resumeSubHeadingListEnd
%-----------Responsibility-----------------
\section{A Day Of My Office Life}
\resumeSubHeadingListStart
   \item{
    \textbf{}{I am a Java Developer with 8 years of experience having proficient knowledge in Data Structure, Algorithms, and System Design. I am leading a few functionalities and modules in Navigator from all perspectives like designing, development, deployment, performance, code quality, and  production support. My responsibility includes working closely with the product owner to understand the new requirement, planning for development, and taking responsibility to deliver it end to end.}}
\resumeSubHeadingListEnd
%
%--------Tech SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Java, SQL, JavaScript, C++}
     \hfill
   }
    \item{
     \textbf{Tools \& Framework}{: Kubernetes, Docker, Cloud Foundry, Spring Boot, Hibernate, SQL, Spring Reactive, Restful Web Service, SOAP Web Service, Maven, Camunda BPMN, Jenkins, Netty Server, Tomcat Server, Oracle, JSP, Servlet, J2EE, IntelliJ, Eclipse, VS Code, Zipkin, Dynatrace, Redis, JMeter, Graphana, Splunk, Kibana, GraphQL}
   }
    \item{
     \textbf{Good knowledge of designing large-scale systems.}{}
     \hfill
   }
   \item{
     \textbf{Proficiency in OOPS principles, Multithreading Concept, Functional Programming.}{}
     \hfill
   }
    \item{
     \textbf{Proficient knowledge of Spring Framework.}{}
     \hfill
   }
    \item{
     \textbf{Basic Knowledge }{: Html, CSS, React, Angular JS, Kafka, RabbitMQ, MongoDB, Elastic Search, Redis, SSO Login, Security, DevOps, Monitoring tools, Traceability tools}
     \hfill
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
